---
title: "split_data"
author: "James Hill"
date: "13/11/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

## Splitting Data

In order to reduce the amount of data the application handles we will split it.
We will load the data in then split into 2 separate tables:

- Match data
- Play data

```{r split_data}

nba_data <-
  readr::read_csv(
    here::here("dev", "data", "source_data", "free_throws.csv"),
    col_types =
      readr::cols(
        end_result = readr::col_character(),
        game = readr::col_character(),
        game_id = readr::col_double(),
        period = readr::col_double(),
        play = readr::col_character(),
        player = readr::col_character(),
        playoffs = readr::col_character(),
        score = readr::col_character(),
        season = readr::col_character(),
        shot_made = readr::col_double(),
        time = readr::col_character()
      )
  ) |>
  dplyr::distinct()

```

## Match Data

Match data contains information about the matches but not individual shots.
There is a large amount of this data duplicated in the original file.
We will also split some of the text columns to allow for finer analysis.

```{r create_match_data}

match_data <-
  nba_data |>
  dplyr::group_by(
    game_id,
    game,
    end_result,
    season,
    playoffs
  ) |>
  dplyr::summarise(
    .groups = "drop_last",
    total_free_throws = dplyr::n(),
    successful_free_throws = as.integer(sum(shot_made)),
    pcnt_successful_free_throws = successful_free_throws / total_free_throws
  ) |>
  dplyr::ungroup() |>
  dplyr::distinct() |>
  tidyr::separate(col = game, into = c("team_away", "team_home")) |>
  tidyr::separate(
    col = end_result,
    into = c("team_away_score", "team_home_score")
  ) |>
  dplyr::mutate(
    game_id = as.integer(game_id),
    team_away_score = as.integer(team_away_score),
    team_home_score = as.integer(team_home_score)
  ) |>
  dplyr::arrange(
    season,
    playoffs,
    game_id
  )

```

Now we save the Match data:

```{r save_match_data}

saveRDS(
  match_data,
  file = here::here("dev", "data", "app_data", "data_match.Rds")
)

saveRDS(
  match_data,
  file = here::here("inst", "extdata", "data_match.Rds")
)

```

## Play Data

Play data contains information about the individual shots.

```{r create_play_data}

play_data <-
  nba_data |>
  tidyr::separate(
    time,
    into = c("minutes_remaining", "seconds_remaining"),
    sep = ":",
    remove = FALSE
  ) |>
  dplyr::mutate(
    game_id = as.integer(game_id),
    period = as.integer(period),
    shot_made = as.logical(shot_made),
    minutes_remaining = as.integer(minutes_remaining),
    seconds_remaining = as.integer(seconds_remaining)
  ) |>
  dplyr::select(
    game_id,
    period,
    player,
    shot_made,
    minutes_remaining,
    seconds_remaining
  ) |>
  dplyr::arrange(
    game_id,
    period,
    desc(minutes_remaining),
    desc(seconds_remaining)
  )

```

Now we save the Play data:

```{r save_play_data}

saveRDS(
  play_data,
  file = here::here("dev", "data", "app_data", "data_play.Rds")
)

saveRDS(
  play_data,
  file = here::here("inst", "extdata", "data_play.Rds")
)

```
